Optimal (Multiway) Spatial Joins

### 2024-06-06 msj.tex
yufei

\extraspacing {\underline{\em Example 4.1.}} To illustrate our algorithm, we will utilize the running example in Figure~\ref{fig:hv:type1:ex}a, where $k = 4$, and $R_1 = \set{\alpha}$ (the solid rectangle), $R_2 = \set{\beta_2, \beta_2}$ (the dashed rectangles), $H$ $=$ $\set{h_1,$ $h_2,$ $..., h_6}$, and $V = \set{v_1, v_2, ..., v_5}$. The set $\J_1$ contains the following tuples: $(\alpha, \beta_2, h_2, v_3)$, $(\alpha, \beta_2, h_2, v_5)$, $(\alpha, \beta_2, h_5, v_3)$, and $(\alpha,$ $\beta_2, h_5, v_6)$. \done

>>>>

\extraspacing {\underline{\em Example 4.1.}} To illustrate our algorithm, we will utilize the running example in Figure~\ref{fig:hv:type1:ex}a, where $k = 4$, and $R_1 = \set{\alpha}$ (the solid rectangle), $R_2 = \set{\beta_2, \beta_2}$ (the dashed rectangles), $H$ $=$ $\set{h_1,$ $h_2,$ $..., h_6}$, and $V = \set{v_1, v_2, ..., v_5}$. The set $\J_1$ contains the following tuples: $(\alpha, \beta_2, h_2, v_3)$, $(\alpha, \beta_2, h_2, v_5)$, $(\alpha, \beta_2, h_5, v_3)$, and $(\alpha,$ $\beta_2, h_5, v_5)$. \done
